Sperm should evolve to make female meiosis fair.

### 2014-05-21 writeup_and_notes/signif_statement.tex
edited signif down to 119

\begin{document}
Female meiosis is the time when alleles can directly modify their transmission. Benefits to alleles that succeeds in this competition and collateral damage to organismal fitness likely shaped basic features of female reproduction. However, the observation that fertilization is often required for the completion of female meiosis appears incompatible with this view. In fact, this fertilization requirement seems to presents an opportunity for sperm-acting alleles to distort the in their own favor, creating an additional arena for conflict. We show that, counterintuitively, the opposite is true, sperm are usually selected to ensure that female meiosis is fair. Intuitively this comes about because sperm immediately suffer the company they keep in the zygote, and it is in sperm's interests to enforce fairness in female meiosis. The wide-spread requirement of fertilization to complete female meiosis may represent a long-term collaboration between sperm and mothers to ensure the production of fit offspring.
\end{document}

>>>>

\begin{document}
Meiosis is the time when alleles compete to ensure their transmission at the expense of organismal fitness, and many features of meiosis may have evolved to reduce competition. The observation that fertilization is often required for the completion of female meiosis appears incompatible with this view; sperm-acting alleles could distort female meiosis in favor, creating an additional conflict. Counterintuitively, we show that sperm are selected to ensure a fair female meiosis. This comes about because sperm immediately suffer the result of cheating, and so it is in sperm's interests to enforce fairness in female meiosis.  The requirement of fertilization to complete female meiosis may represent a long-term collaboration between sperm and mothers to ensure the production of fit offspring.
\end{document}
